Correcting K-correction: dark energy is based on a math error from 1930

### 2025-01-05 paper/dark_energy_corrections.tex
AAS doesn't like stacked fractions...

\begin{itemize}
  \item The energy of a wave is inversely proportional to its wavelength; thus a
  redshift of $z$ means the amount of energy per photon is reduced by a factor
  of $\frac{1}{1+z}$.

@@

\begin{figure}
  \includegraphics[width=.75\linewidth, height=0.75\vsize]{k_equation_flow.png}
  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
  are able to observe a SnIa in the redshifted observation frame, but we want
  to compute the magnitude in the rest frame as if no redshift has occurred.
  This computation starts with $F(\lambda$, the spectral energy density that
  describes the expected luminosity in the rest frame. Using the SED, we can
  compute the photon density $F'(\lambda)$ for the rest frame. We show the
  process of computing $R'(\lambda$, the photon density in the observation
  frame, in three phases starting at the top right of the figure. First we
  stretch the photon density, but this step inflates counts. In the second
  step, we correct for the inflated counts by multiplying by $\frac{1}{1+z}$;
  at this point, the total count equals the total count of $F'(\lambda)$.
  Finally, in the third step we finish calculating the observation frame photon
  density $R'(\lambda)$ by accounting for time dilation, which also reduces
  photon counts by a factor of $\frac{1}{1+z}$.  Given the rest frame and
  observation frame photon densities, we can compute the expected ratio of
  photons by totalling the area under the curves in the two panels at the
  bottom of the graph. This example does not show the process of converting
  photon flux to magnitude, nor does it address the zero-point correction.
  }
  \label{fig:k-example}
\end{figure}

@@

To convert the spectral energy density $F$ to the photon density $F'$, we need
to use the Plank relation $E = \frac{hc}{\lambda}$ where $E$ is the energy, $h$
is Planck's constant, and $c$ is the speed of light. This gives us

@@

It is useful to consider whether the term $\frac{P'_y}{P'_x}$ is correct or if
it should be inverted, but if we rewrite Equation \ref{eq:as_flux} as

@@

\begin{equation}
\begin{aligned}
  K'_{xy} &= \frac{P'_x}{P'_y} \times \frac{\mathcal{F}_x}{\mathcal{F}_y} \\
         &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
                   {\int R'(\lambda) S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
                   {\int F'(\frac{\lambda}{1+z}) \times \frac{1}{(1 + z)^2} S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
              \frac{\int \frac{\lambda}{hc} F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{(1+z)hc} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} .
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
\label{eq:K2k}
  K_{xy} &= 2.5\text{log}(K'_{xy}) \\
         &= 2.5\text{log}\left(
            \frac{P'_x}{P'_y} \times (1 + z)^2 \times
            \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                 {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}\right) \\
         &= 2.5 \left(
            \text{log} \left( \frac{P'_x}{P'_y} \right)
            + \text{log}( {(1 + z)^2})
            + \text{log}\left( \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}
            \right) \right) \\
         &= 2.5 \text{log} \left( \frac{P'_x}{P'_y} \right)
            + 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
            - P_x + P_y .
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  K_{xy} &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
            - P_x + P_y \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
            + 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
            - 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
         &= 2.5 \text{log} \left(
              \frac{\int \lambda \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
                   {\int \lambda \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
             \right)
            + 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) .
\end{aligned}
\end{equation}

>>>>

\begin{itemize}
  \item The energy of a wave is inversely proportional to its wavelength; thus a
  redshift of $z$ means the amount of energy per photon is reduced by a factor
  of $1 / (1+z)$.

@@

\begin{figure}
  \includegraphics[width=.75\linewidth, height=0.75\vsize]{k_equation_flow.png}
  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
  are able to observe a SnIa in the redshifted observation frame, but we want
  to compute the magnitude in the rest frame as if no redshift has occurred.
  This computation starts with $F(\lambda$, the spectral energy density that
  describes the expected luminosity in the rest frame. Using the SED, we can
  compute the photon density $F'(\lambda)$ for the rest frame. We show the
  process of computing $R'(\lambda$, the photon density in the observation
  frame, in three phases starting at the top right of the figure. First we
  stretch the photon density, but this step inflates counts. In the second
  step, we correct for the inflated counts by multiplying by $1/(1+z)$;
  at this point, the total count equals the total count of $F'(\lambda)$.
  Finally, in the third step we finish calculating the observation frame photon
  density $R'(\lambda)$ by accounting for time dilation, which also reduces
  photon counts by a factor of $1/(1+z)$.  Given the rest frame and
  observation frame photon densities, we can compute the expected ratio of
  photons by totalling the area under the curves in the two panels at the
  bottom of the graph. This example does not show the process of converting
  photon flux to magnitude, nor does it address the zero-point correction.
  }
  \label{fig:k-example}
\end{figure}

@@

To convert the spectral energy density $F$ to the photon density $F'$, we need
to use the Plank relation $E = hc / \lambda$ where $E$ is the energy, $h$
is Planck's constant, and $c$ is the speed of light. This gives us

@@

It is useful to consider whether the term $P'_y / P'_x$ is correct or if
it should be inverted, but if we rewrite Equation \ref{eq:as_flux} as

@@

\begin{equation}
\begin{aligned}
  K'_{xy} &= \frac{P'_x}{P'_y} \times \frac{\mathcal{F}_x}{\mathcal{F}_y} \\
         &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
                   {\int R'(\lambda) S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
                   {\int F'(\lambda / (1+z)) \times (1 / (1 + z)^2) S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
              \frac{\int (\lambda / hc) F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / ((1+z)hc)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z) F(\lambda / (1+z)) S_y(\lambda) d\lambda} .
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
\label{eq:K2k}
  K_{xy} &= 2.5\text{log}(K'_{xy}) \\
         &= 2.5\text{log}\left(
            \frac{P'_x}{P'_y} \times (1 + z)^2 \times
            \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                 {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda}\right) \\
         &= 2.5 \left(
            \text{log} \left( \frac{P'_x}{P'_y} \right)
            + \text{log}( {(1 + z)^2})
            + \text{log}\left( \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                                    {\int (\lambda / (1+z)) F((\lambda)/ (1+z)) S_y(\lambda) d\lambda}
            \right) \right) \\
         &= 2.5 \text{log} \left( \frac{P'_x}{P'_y} \right)
            + 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right)
            - P_x + P_y .
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  K_{xy} &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right)
            - P_x + P_y \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\ &\ 
            + 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
            - 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
         &= 2.5 \text{log} \left(
              \frac{\int \lambda \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
                   {\int \lambda \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
             \right)
            + 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) .
\end{aligned}
\end{equation}
